How I use R Markdown to write research papers

### 2020-12-21 text/20/markdown-papers.Rmd
Added nas-reproducibility.md

---
title: "How I use R Markdown to write research papers"
source: "New"
categories:
- Blog post
tags:
- Writing research papers
output: html_document
bibliography: rmarkdown-papers.bib
csl: biomed-central.csl
nocite: |
  @ziemann-2016, @zeeberg-2004
---

@@

The bibliography always appears at the end of the document.

>>>>

---
title: "How I use R Markdown to write research papers"
source: "New"
categories:
- Blog post
tags:
- Writing research papers
output: html_document
---

@@

The bibliography always appears at the end of the document. I'm not showing a bibliography for technical reasons, but it is pretty easy.
